---
title: "Assignment 2"
author: Daniel Bonnery, Max Kramkimel, Augustin Poissonnier
date: Dec 5, 2023
output: github_document
---

# Bayesian Statistics, Assignment 2




## Results


```{r,echo=FALSE,results="hide"}
"R"|>list.files(full.names = TRUE)|>sapply(FUN = source)
"samples_of_q.rda"|>load()|>get()->q
tt=200
burning=1000
```

### Plot 1

```{r,echo=FALSE}
plot_q_1_f(q,tt,burning)
```

### Plot 2

```{r,echo=FALSE}
plot_q_2_f(q,tt,burning)
```


## How to run 

### Install the following packages:

```{r,echo=FALSE,message=FALSE,warning=FALSE,error=FALSE,results=FALSE}
renv::dependencies("R")$Package|>unique()|>sort()|>setdiff(c(
  "montruc","LocustAnalysis","synthpop"))|>paste(collapse = ", ")->xx
```

`r xx`

### Copy and execute the project:

- Clone the project to a local repository
via:

```{r,eval=FALSE}
system("git clone https://github.com/Augustin202/Stat_bayes.git")
```

- open the .rproj file in rstudio
- run:

```{r,eval=FALSE}
source(main.R)
```

## R code

The R code consists a file R/functions.R that contains all necessary functions to run the main code, a main.R file that will run the main program. The main file generates the data, draw samples of q, creates plots and compiles the Rmd file to create this markdown file, and an Rproj file, all available on github there:.


### main.R

```{r, eval=FALSE, file = 'main.R'}
```


### R/functions.R

```{r, eval=FALSE,file = 'R/functions.R'}
```

