---
title: "Assignment 2"
author: Daniel Bonnery, Max Kramkimel, Augustin Poissonnier
date: Dec 5, 2023
output: github_document
---

# Bayesian Statistics, Assignment 2

## Results


```{r,echo=FALSE,results="hide",warning=FALSE,message=FALSE}
knitr::opts_chunk$set(error=FALSE, warning=FALSE,comment=FALSE,message=FALSE)
```

```{r,echo=FALSE,results="hide",warning=FALSE,message=FALSE,comment=FALSE}
"R"|>list.files(full.names = TRUE)|>sapply(FUN = source)
"samples_of_q.rda"|>load()|>get()->q
tt=200
k=100
burning=1000
```

### Plot 1

```{r,echo=FALSE}
library(scales)
plot_q_1_f(q,k,burning)+
     scale_x_log10(breaks = c(.01,.02,.05,.1,.2,.5,1))
plot_q_1_f(q,k,burning)+
     scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x)))
```

We plot the histograms of the empirical means of q by values of s and R2y.
The red line represents s/k. The blue line represents the mean of the empirical means. We use a log10 scale for the x axis.

### Plot 2

```{r,echo=FALSE}
plot_q_2_f(q,tt,burning)
```


We plot the histograms of the empirical means of q by values of s and R2y.
The red line represents s/k. The blue line represents the mean of the empirical means. We use a log10 scale for the x axis.

## How to run 

### Install the following packages:

```{r,echo=FALSE,message=FALSE,warning=FALSE,error=FALSE,results=FALSE}
renv::dependencies("R")$Package|>unique()|>sort()|>setdiff(c(
  "montruc","LocustAnalysis","synthpop"))|>paste(collapse = ", ")->xx
```

`r xx`

### Copy and execute the project:

- Clone the project to a local repository
via:

```{r,eval=FALSE}
system("git clone https://github.com/Augustin202/Stat_bayes.git")
```

- open the .rproj file in rstudio
- run:

```{r,eval=FALSE}
source(main.R)
```
